### 2016-09-26 projects_that_depend_on_sympy.tex
\ref the table
Change OctSymPy back to Octave Symbolic
As per @cbm755.

There are several projects that depend on SymPy as a library for implementing
a part of their functionality. A selection of these projects are listed below:

@@

\href{https://github.com/cbm755/octsympy}{\textbf{OctSymPy}}~\cite{OctSymPy} &  &
  The OctSymPy package adds symbolic calculation features
  to GNU Octave. These include common CAS tools such
  as algebraic operations, calculus, equation solving, Fourier and
  Laplace transforms, variable precision arithmetic, and other features. \\

>>>>

There are several projects that depend on SymPy as a library for implementing
a part of their functionality. A selection of these projects are listed in
Table~\ref{projects-table}.

@@

\href{http://octave.sourceforge.net/symbolic}{\textbf{Octave Symbolic}}~\cite{OctSymPy} &  &
  The OctSymPy package adds symbolic calculation features
  to GNU Octave. These include common CAS tools such
  as algebraic operations, calculus, equation solving, Fourier and
  Laplace transforms, variable precision arithmetic, and other features. \\
